VIP-193: Committee-Based POA

### 2019-11-07 article.tex
fix ref

A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$.

\begin{algorithm}[H]
\caption{Procedure for validating a block.}
\label{alg:block-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \State Verify $u_i$'s endorsement by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a lower bound for the probability of launching a $k$-block DSA.

@@

Therefore, the probability of adversaries controlling the committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$. Table~\ref{tab:k-prob} lists the values of this probability with different inputs. We set $f$ according to the Byzantine Fault Tolerance~(BFT) assumption. It is a security assumption that is considered reasonable and widely used in practice.

>>>>

A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$. Algorithm~\ref{alg:block-valid} describes how to validate a block generated in round $r$. To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.

\begin{algorithm}[H]
\caption{Procedure for validating a block generated in round $r$.}
\label{alg:block-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \State Verify $u_i$'s endorsement by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

\subsection{Double-Spending Attack}
The main goal of introducing the committee mechanism is to make it more difficult for adversaries to cause inconsistency. Perhaps the most damaging of such attacks is the double-spending attacks~(DSAs)~\cite{Sat08} where adversaries are allowed to take control of a few consecutive consensus rounds such that they can produce two parallel branches to launch a DSA. Here we are going to infer a lower bound for the probability of launching a $k$-block DSA. We focus on solving the DSA in a practical synchronous network setting, where we assume that a message be broadcast through the gossip protocol and reach the whole network with some bounded delay.

@@

Therefore, the probability of adversaries controlling the committee for $k$ consecutive rounds is $F(p_\epsilon,d,f)^k$. Table~\ref{tab:dsa-prob} lists the values of this probability with different inputs. We set $f$ according to the Byzantine Fault Tolerance~(BFT) assumption. It is a security assumption that is considered reasonable and widely used in practice.
